---
title: "Cabinet handle removal"
subtitle: 'Sound power comparison'
author: "Mirella L Thomazini, Andreyson Jambersi, Thiago Galavotti, Samuel B Baco"
output:
  pdf_document:
    includes:
      in_header: latex/headFooter.tex
      before_body: latex/before_body.tex
  html_notebook: default
  html_document:
    df_print: paged
bibliography: references.bib
---

```{=html}
<style>
body {text-align: justify}
</style>
```
\newpage

\thispagestyle{plain}

\tableofcontents

\newpage

\thispagestyle{plain}

# INTRODUCTION

\newpage

\thispagestyle{plain}

# 1 DATA AND PACKAGE LOADING

## 1.1 Package loading

```{r PACKAGELOADING, message=F, warning=F}

library(tidyverse)
library(knitr)
library(factoextra)
library(VCA)
library(lme4)
library(car)
library(brms)
library(bayesplot)
library(tidybayes)

# Auxiliar functions

source("~/R/cabinetHandle/functions/brms_mdl_check.R")
source("~/R/cabinetHandle/functions/brms_pred_post.R")

```

```{r KNITROPTIONS}

opts_chunk$set(message = F, warning = F, dpi = 300, dev = "ragg_png")

options(scipen = 999)

```

# 2 DATA LOADING AND WRANGLE

```{r DATALOADING, message=F, warning=F}

df <-
  read_csv("dataSets/data.csv", 
           locale = locale(decimal_mark = ",")
  ) %>% 
  select(
    c("Product Model", "Cabinet Condition", "Sample"), 15:20
  ) %>% 
  rename(
    'prod' = "Product Model",
    'handle' = "Cabinet Condition",
    'sample' = 'Sample',
    'soundP' = "Y1 = Sound Power [dB]",
    'wuVib1' = "WU vibration 1",
    'wuVib2' = "WU vibration 2",
    'wuVib3' = "WU vibration 3",
    'cabVib' = "Cabinet Vibration",
    'rpm' = "Y3 = RPM"
  ) %>% 
  mutate(
    prod = case_when(
      prod == 1 ~ -1,
      T ~ 1
    ),
    handle = case_when(
      handle == '-' ~ '-1',
      T ~ '1'
    ),
    handle = as.numeric(handle),
    sample = as.factor(sample)
  )

```


# 3 PRINCIPAL COMPONENT ANALYSIS

## 3.1 Calculation

```{r PCA, message=F, warning=F}

pca <-
  princomp(
    df %>% 
      select(wuVib1, wuVib2, wuVib3, cabVib, rpm),
    cor = T,
    scores = T
  )

print(pca)

dfFinal <-
  df %>% 
  mutate(
    p1 = pca$scores[ ,'Comp.1'],
    p2 = pca$scores[ ,'Comp.1']
  )

```

## 3.2 Graphical evaluation

```{r PCAGRAPH, message=F, warning=F}

# Scree plot

fviz_eig(pca) +
    labs(
    title = 'Scree plot'
  ) +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    plot.title = element_text(face = 'bold')
      
  )

# Loading plot

fviz_pca_var(pca, repel = T) +
  labs(
    title = 'PCA loadings',
    subtitle = 'Product sound power | covariates'
  ) +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    plot.title = element_text(face = 'bold')
      
  )

```
# 4 FREQUENTIST ANALYSIS

## 4.1 Graphical analysis

```{r VARIABILITY}

varPlot(
        soundP ~ prod + handle + sample,
        Data = as.data.frame(dfFinal),
        htab = 0.8,
        Title = list(
                main = 'Cabinet handle removal | Sound power',
                adj = 0
        ),
        YLabel = list(
                text = ''
        ),
        MeanLine = list(
                var = c('prod', 'handle', 'sample'),
                col = c('blue', 'red', 'green')
        )
)

```

## 4.2 Mixed model

```{r FREQMIXMODEL}

dfCat <-
  dfFinal %>% 
  mutate(
    prod = case_when(
      prod == -1 ~ 0,
      T ~ 1
    ),
    handle = case_when(
      handle == -1 ~ 0,
      T ~ 1
    ),
    prod = as.character(prod),
    handle = as.character(handle)
  )

mixModFull <-
  lmer(
    soundP ~ p2 + prod + handle + (1 | sample),
    data = dfCat,
    control = lmerControl(optimizer = "Nelder_Mead")
  )

summary(mixModFull, correlation = F)

```

# 4.2 Bayesian analysis

## 4.2.1 Stanvars

```{r GAMMA}

# Allow shape = sd(y) / 2 and rate = 2 * sd(y)

gamma_a_b_from_omega_sigma <- function(mode, sd) {
        
        if (mode <= 0) stop("mode must be > 0")
        
        if (sd   <= 0) stop("sd must be > 0")
        
        rate <- (mode + sqrt(mode^2 + 4 * sd^2)) / (2 * sd^2)
        
        shape <- 1 + mode * rate
        
        return(list(shape = shape, rate = rate))
}

```


```{r STANVARS}

# Stanvar parameters

yMean <- mean(dfFinal$soundP)

ySd <- sd(dfFinal$soundP)

yOmega <- ySd / 2

ySigma <- 2 * ySd

sr <- 
        gamma_a_b_from_omega_sigma(
                mode = yOmega, 
                sd = ySigma
        )

# Stanvars definition

stanVars <-
        stanvar(yMean, name = 'mean_y') + 
        stanvar(ySd, name = 'sd_y') + 
        stanvar(sr$shape, name = 'alpha') + 
        stanvar(sr$rate, name = 'beta') + 
        stanvar(1/29, name = 'one_over_twentynine')

```

## 4.2.2 Linear fit

```{r BAYESMODEL}

bayesMdl <-
        brm(
                data = dfCat,
                family = student,
                soundP ~ p2 + prod + handle + (1 | sample),
                prior = c(
                        # Prior to intercept (Beta 0)
                        prior(normal(mean_y, sd_y*10), 
                              class = Intercept),
                        # Prior for numerical var coef
                        prior(normal(mean_y, sd_y*10), class = b),
                        # Prior for categorical var coef
                        prior(gamma(alpha, beta), class = sd),
                        # Prior for residual variance (student distribution)
                        prior(normal(0, sd_y), class = sigma),
                        # Prior for student distribution df parameter
                        prior(exponential(one_over_twentynine), 
                              class = nu)
                ),
                stanvars = stanVars,
                iter = 200000,
                warmup = 4000,
                chains = 4,
                cores = 4,
                seed = 123456,
                #control = list(adapt_delta = .99),
                thin = 100,
                backend = "cmdstanr", 
                threads = threading(2)
        )

summary(bayesMdl)

```
# 4.3 Handle contrast 

```{r HANDLECONSTRAST}

# Extract chains

chains <-
  as_draws_df(bayesMdl)

# Create contrast information

contrastData <-
  chains %>% 
  select(b_Intercept, b_handle1) %>%
  rename(
    'withoutHandle' = 'b_Intercept'
  ) %>% 
  mutate(
    withHandle = withoutHandle + b_handle1,
    contrast = withoutHandle - withHandle
  )

# Plot contrast

contrastData %>% 
  ggplot(aes(x = contrast)) + 
  geom_histogram() +
  geom_vline(xintercept = 0) + 
  labs(
    title = 'Soundpower contrast',
    subtitle = 'Contrast = without handle - with handle',
    x = 'Contrast',
    y = ''
  ) +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    plot.title = element_text(face = 'bold')
      
  )

# 95% High density interval

contrastData %>% 
        median_qi(contrast, .width = 0.95) %>%
        select(contrast, .lower, .upper) %>%
        rename('Median' = 'contrast',
               'Lower 50HDI' = '.lower',
               'Upper 50HDI' = '.upper') %>% 

        kable(
                caption = 'Soundpower contrast wihtout handle',
                format.args
                = list(
                        scientific = F,
                        digits = 2
                )
                
        )

# Plot 95% HDI Intervals for contrast

mcmc_intervals(
        contrastData, 
        pars = c('contrast')
) +
        labs(
                title = 'Soundpower contrast',
                subtitle = 'Contrast = Without handle - with handle'
        ) +
        theme(
                title = element_text(face = 'bold'),
                plot.subtitle = element_text(face = 'plain')
        )


```

# APPENDIX

## A.1 Bayes model check

### Chains convergence

```{r CHAINSCONVERGENCE}

brms_mdl_check(bayesMdl, nvar = 7, ncol = 3)

```

### Posterior predictive

```{r POSTPRED}

brms_pred_post(dfCat$soundP,bayesMdl, ndens = 128)

```


\newpage

\thispagestyle{plain}

# SESSION INFO

```{r SESSIONINFO}

sessionInfo()

```

\newpage

\thispagestyle{plain}

# BIBLIOGRAPHY